Sakura Blossom Prediction Model for Japan

### 2024-12-02 paper/paper.qmd
finish!

---
title: "Sakura Blossom Prediction Model for Japan"
subtitle: "Forecasting Sakura Blossom Using Bayesian Hierarchical Regression"
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: long
abstract: "This study employs a Bayesian hierarchical linear regression model to predict sakura blooming dates across Japan by analyzing key predictors such as temperature, latitude, and longitude. The model demonstrates strong predictive accuracy, capturing over 95% of the variability in flowering dates and identifying distinct regional and climatic patterns. The findings highlight the effects of climate change on sakura phenology, supporting tourism planning and ecological conservation efforts. Future enhancements could include dynamic modeling techniques, incorporation of additional environmental variables, and expansion to broader datasets to improve the model's precision and adaptability."
format: pdf
toc: true
number-sections: true
bibliography: references.bib

@@

library(tidyverse)
library(dplyr)
library(here)
library(readr)
library(lubridate)
library(rvest)
library(palmerpenguins)
library(maps)
library(ggplot2)
library(knitr)
library(arrow)
library(rstanarm)
library(plotly)
library(patchwork)
library(tidyr)
library(bayesplot)
library(gridExtra)
library(kableExtra)
library(broom.mixed)

@@

For performing the analysis, we utilized several R packages. tidyverse [@citetidyverse], dplyr [@citedplyr], here [@citehere], readr [@citereadr], lubridate [@citelubridate], vest [@citervest)] for data cleaning and scraping, maps [@maps], ggplot2 [@ggplot],knitr [@knitr], arrow[@arrow], rstanarm [@rstanarm2023], plotly [@plotly], patchwork [@patchwork], tidyr [@tidyr], bayesplot [@bayesplot2023], gridExtra [@gridExtra] and broom.mixed [@broom] for data building and model preparation .

@@

## Measurement
Our dataset, sourced from Alex Cookson's work [@Alex2020sakura], integrates temperature data scraped from the Japan Meteorological Agency [@Japanclimate]. The merged dataset contains 5,387 observations, aggregating average temperatures for the corresponding regions and flowering months. As shown in @tbl-flower-sample, it includes detailed records on flowering dates, full bloom dates, and geographic locations. By compiling flowering times and geographic information for sakura blossoms across Japan from 1953 to 2019, this dataset provides robust foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.

@@

# Display the sample as a clean table
kable(sakura_sample, 
      col.names = c("ID", "Location", "Latitude", "Longitude", "Year", "Month",
                    "Flower Day", "Full Bloom Day", "Mean Temp"))
```
For historical sakura data provided by Prof. Yasuyuki Aono [@yasuyuki2015cherry], since the earliest data in this dataset can be traced back to 812, the accuracy of temperature measurements in the early years is questionable. Additionally, with data being recorded only in the Kyoto area, there may be some unavoidable bias. Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will serve solely as a comparison to help us understand the historical situation which we will discuss at @sec-dis.

@@

```{r}
#| label: tbl-flower-sta   # For citation in Quarto
#| tbl-cap: "Statistic Summary of Flowering and Full Blossom Day"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false

# Generate the summary for flowering day
flowering_day_summary <- summary(sakura_data$flower_day_in_numeric)
flowering_day_summary_df <- data.frame(
  Statistic = names(flowering_day_summary),
  `Flowering Day` = as.numeric(flowering_day_summary)
)

# Generate the summary for full bloom day
full_bloom_day_summary <- summary(sakura_data$full_bloom_day_in_numeric)
full_bloom_day_summary_df <- data.frame(
  Statistic = names(full_bloom_day_summary),
  `Full Bloom Day` = as.numeric(full_bloom_day_summary)
)

@@

# Display the combined summary table
kable(
  combined_summary_df,
  caption = ""
)

@@

## Predictor variables
In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis.

### Average Temperature of the Flowering Month
The first variable is the average temperature of the flowering month (month_mean_temp). "The thermal ecology of Flowers" by Dr.Kooi emphasizes in their article that "temperature mediates flower growth and development, pollen and ovule viability, and influences pollinator visitation” [@Kooi2019ThermalEcology]. Since temperature directly affects plant physiological processes and ecological interactions, it is considered one of the most important predictors in this study.

### Geographical Information (Latitude and Longitude)
The second variable is geographical information, including latitude and longitude, which provides precise spatial details about the recording locations in different regions. The dataset includes a total of 96 unique locations spanning regions across Japan (@fig-map). Variations in latitude and longitude are expected to influence blooming times, largely due to their effect on climatic factors such as temperature, sunlight exposure, and climate condition

@@

### Years under Global Warming
Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included as a random effect in the model. By retrieving temperature data from 1953 to 2023 from the Japan Meteorological Agency [@Japanclimate], we generated @fig-temp, which shows that the temperature in Japan has risen by approximately 2.73 degrees Celsius compared to 1953. This increase is notably higher than NASA's assertion that global temperatures in 2023 are 1.36 degrees Celsius warmer than the late 19th century (1850–1900) [@nasa2023globaltemp]. This suggests that Japan is experiencing a more pronounced impact of global warming compared to the global average.

@@

### Latitude and Longitude with Temperature
@fig-cor illustrates how temperatures vary across different locations based on their geographical coordinates. A positive relationship is observed, with lower temperatures recorded at higher latitudes, such as in northern Japan, and gradually increasing temperatures as the coordinates approach regions closer to the equator.
```{r}
#| label: fig-cor   # For citation in Quarto
#| fig-cap: "Temperature Variation"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center
#| 
# Create a 2D scatter plot with color indicating temperature
ggplot(sakura_data, aes(x = latitude, y = longitude, color = month_mean_temp)) +
  geom_point(size = 3) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(
    title = "Temperature Variation with Latitude and Longitude",
    x = "Latitude",
    y = "Longitude",
    color = "Mean Temp (°C)"
  ) +
  theme_minimal()
```

@@

## Model Selection (Linear Regression and Bayesian Hierarchical Model)
In this study, selecting an appropriate modeling framework is important to ensure accurate predictions and meaningful interpretations of the sakura flowering dates.

@@

## Model set-up
This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR], with the default priors provided by rstanarm @rstanarm. The analysis_sakura_data dataset is divided into training and testing sets, with 80% allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance. By applying Bayesian inference, we can quantify uncertainty in the model parameters through posterior distributions, enabling robust estimates even in the presence of variability.

@@

## Result of the Analysis Data
@fig-rela_result presents the correlation between each predictor variable—latitude, longitude, and monthly mean temperature—and flowering day.

@@

## Result of the Prediction Model
### Performance Overview Analysis

@@

Longitude, by contrast, has a smaller and less certain effect. The coefficient of -0.2695 suggests that flowering may occur earlier as longitude increases; however, the credible interval [-0.7217, 0.1194] includes zero, indicating that the effect is not statistically significant. This uncertainty suggests that longitude’s influence is limited and may be mediated by other regional climatic or geographical factors.
```{r}
#| label: tbl-fix   # For citation in Quarto
#| tbl-cap: "Fixed Effects Coefficients with 95% Credible Intervals"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center

@@

The variance explained by the random effects with adjust \(R^2\) = \(R^2\) = 1.000 confirms that the model perfectly partitions the variability attributed to year and region. Year-based random effects capture temporal patterns,such as the impact of global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes. Region-based random effects, on the other hand, account for spatial heterogeneity influenced by geographic and environmental differences, such as latitude and local climate conditions. Together, these random effects ensure that the model accurately reflects both temporal and spatial dynamics.
```{r}
#| label: tbl-ram   # For citation in Quarto
#| tbl-cap: "Performance Metrics for Random Effects"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center
#To be note this code is used for preparing the following data, it will not return ant
# === Step 1: Extract Random Effects ===
# Extract station-level and year-level random effects
random_effects <- ranef(flower_model, condVar = TRUE)

@@

## Interpretation 
Temperature is considered the most influential predictor of sakura flowering dates, with even minor increases in monthly mean temperatures significantly accelerating blooming. This finding aligns with ecological theories describing phenological shifts driven by global warming. Specifically, a 1°C rise in temperature shifts flowering earlier by an average of 0.33 days, demonstrating the exceptional sensitivity of sakura phenology to climatic variations. It is also a microcosm of the impact of climate change on biological events.

@@

## Sakura Blossom in Modern Situation (1953-2019)
@fig-1953 presents the blooming dates of sakura across Japan from 1953 to 2019( displayed in numeric form as days of the year). Overall data points exhibit a substantial variation. The red smooth trend line indicates a clear shift toward earlier blooming over time, particularly since the late 20th century, imply the influence of global warming on sakura blossom phenology. Notably, the clustering of most data points reflects the inherent stability of Japan's sakura blossom flowering patterns, while significant outliers, such as unusually early blooming events in recent years, may caused by the impact of extreme weather conditions or the introduction of early-blooming sakura blossom varieties.
```{r}
#| label: fig-1953
#| fig-cap: "1953 to 2019 Data (Sourced from Analysis Modern Sakura Data) "
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

## Limitation
Although the model demonstrates strong predictive performance, several limitations must be acknowledged. First, the assumption that all regions respond uniformly to climate variables may oversimplify the complex ecological processes that influence sakura blooming. This approach overlooks important microclimatic variations, such as the urban heat island effect or the unique climates of mountainous regions, which can significantly impact flowering patterns.

@@

## Additional data details {#sec-sam}
###History Data
The historical dataset, shown in @fig-hissam, includes reconstructed March temperatures, the flowering day of the year (DOY), and specific flowering dates for selected years between 812 and 851 CE.
```{r}
#| label: fig-hissam
#| fig-cap: "Sample Historical Sakura Data"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center
# Select a sample of rows from the historical data
sample_history_data <- history_data %>%
  select(year, temp_c_recon, flower_doy, flower_date) %>%
  slice(1:4)  # Select the first 4 rows for demonstration

@@

### Correlation between Each Variable
@fig-heatmap presents the correlation heatmap for the modern sakura dataset, illustrating the relationships between key numerical variables. A notably strong positive correlation (close to 1) is observed between flower_day_in_numeric and full_bloom_day_in_numeric. Latitude and longitude also show moderate to strong positive correlations with flowering indicators, emphasizing the influence of geographic factors on blooming behavior. Among these, latitude exhibits a particularly strong correlation, highlighting its significance in predicting flowering dates.This is consistent with our results in @sec-result. And the variable year showed a weak negative correlation with flowering date, suggesting that flowering may occur earlier in the year under the influence of increasing temperatures due to global warming. 
```{r}
#| label: fig-heatmap
#| tbl-cap: "Correlation Heatmap"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

## Model details {#sec-model-details}
### Posterior predictive check

In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check and the distribution of posterior are show in @fig-pos-dis. 
This shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions. The observed density, represented by the dark blue line, closely matches the predictive densities (lighter blue lines) across most of the distribution, indicating that the model captures the central tendency and major patterns effectively. The primary peak around 80 is well-represented, showing the model's strength in predicting the most common flowering dates. Additionally, the secondary peak around 120 aligns reasonably well, suggesting the model's ability to handle more complex patterns, such as bimodal distributions. However, slight discrepancies are observed in the tails of the distribution, particularly below 40 and above 140, where the predictive densities deviate from the observed data. These divergences indicate potential challenges in capturing extreme values or outliers, which may be addressed by including additional predictors, such as microclimatic conditions or species-specific traits.

```{r}
#| eval: true
#| echo: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
#| warning: false 
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-mcmc-convergence
#| fig-cap: "MCMC Convergence Diagnostics"
#| fig-subcap: ["Trace Plot for Key Parameters", "R-hat Diagnostics"]
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

>>>>

---
title: "Sakura Blossom Prediction Model for Japan"
subtitle: "Forecasting Sakura Blossom Using Bayesian Hierarchical Regression"
author: 
  - Shanjie Jiao
thanks: "Code and data are available at: https://github.com/Jie-jiao05/Sakura-Blossom-Prediction-Model."
date: today
date-format: long
abstract: "This study employs a Bayesian hierarchical linear regression model to predict sakura blooming dates across Japan by analyzing key predictors such as temperature, latitude, and longitude. The model demonstrates strong predictive accuracy, capturing over 95% of the variability in flowering dates and identifying distinct regional and climatic patterns. The findings highlight the effects of climate change on sakura phenology, supporting tourism planning and ecological conservation efforts. Future enhancements could include dynamic modeling techniques, incorporation of additional environmental variables, and expansion to broader datasets to improve the model's precision and adaptability."
format:
  pdf:
    fig-pos: H
toc: true
number-sections: true
bibliography: references.bib

@@

library(tidyverse)
library(dplyr)
library(here)
library(readr)
library(lubridate)
library(rvest)
library(palmerpenguins)
library(maps)
library(ggplot2)
library(knitr)
library(arrow)
library(rstanarm)
library(plotly)
library(patchwork)
library(tidyr)
library(bayesplot)
library(gridExtra)
library(kableExtra)
library(broom.mixed)
library(modelsummary)

@@

For performing the analysis, we utilized several R packages. tidyverse [@citetidyverse], dplyr [@citedplyr], here [@citehere], readr [@citereadr], lubridate [@citelubridate], vest [@citervest)] for data cleaning and scraping, maps [@maps], ggplot2 [@ggplot],knitr [@knitr], arrow[@arrow], rstanarm [@rstanarm2023], plotly [@plotly], patchwork [@patchwork], tidyr [@tidyr], bayesplot [@bayesplot2023], gridExtra [@gridExtra], broom.mixed [@broom], and modelsummary [@modelsummary] for data building and model preparation .

@@

## Measurement

Our dataset, sourced from Alex Cookson's work [@Alex2020sakura], integrates temperature data scraped from the Japan Meteorological Agency [@Japanclimate]. The merged dataset contains 5,387 observations, aggregating average temperatures for the corresponding regions and flowering months. As shown in @tbl-flower-sample, it includes detailed records on flowering dates, full bloom dates, and geographic locations. By compiling flowering times and geographic information for sakura blossoms across Japan from 1953 to 2019, this dataset provides robust foundational data for studying the timing patterns and potential influencing factors of sakura blossom flowering.

@@

# Display the sample as a clean table
kable(sakura_sample, 
      col.names = c("ID", "Location", "Latitude", "Longitude", "Year", "Month",
                    "Flower Day", "Full Bloom Day", "Mean Temp"))
```

For historical sakura data provided by Prof. Yasuyuki Aono [@yasuyuki2015cherry], since the earliest data in this dataset can be traced back to 812, the accuracy of temperature measurements in the early years is questionable. Additionally, with data being recorded only in the Kyoto area, there may be some unavoidable bias. Therefore, when building the prediction model, we will only use modern sakura data for fitting, and historical data will serve solely as a comparison to help us understand the historical situation which we will discuss at @sec-dis.

@@

```{r}
#| label: tbl-flower-sta   # For citation in Quarto
#| tbl-cap: "Statistic Summary of Flowering and Full Blossom Day"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
# Generate the summary for flowering day
flowering_day_summary <- summary(sakura_data$flower_day_in_numeric)
flowering_day_summary_df <- data.frame(
  Statistic = names(flowering_day_summary),
  `Flowering Day` = round(as.numeric(flowering_day_summary), 2)  # Round to 2 decimal places
)

# Generate the summary for full bloom day
full_bloom_day_summary <- summary(sakura_data$full_bloom_day_in_numeric)
full_bloom_day_summary_df <- data.frame(
  Statistic = names(full_bloom_day_summary),
  `Full Bloom Day` = round(as.numeric(full_bloom_day_summary), 2)  # Round to 2 decimal places
)

@@

# Display the combined summary table
library(knitr)
kable(
  combined_summary_df,
)

@@

## Predictor variables

In this study, sakura blooming dates are influenced by multiple environmental and geographical factors, leading to the selection of several key predictor variables for analysis.

### Average Temperature of the Flowering Month

The first variable is the average temperature of the flowering month (month_mean_temp). "The thermal ecology of Flowers" by Dr.Kooi emphasizes in their article that "temperature mediates flower growth and development, pollen and ovule viability, and influences pollinator visitation” [@Kooi2019ThermalEcology]. Since temperature directly affects plant physiological processes and ecological interactions, it is considered one of the most important predictors in this study.

### Geographical Information (Latitude and Longitude)

The second variable is geographical information, including latitude and longitude, which provides precise spatial details about the recording locations in different regions. The dataset includes a total of 96 unique locations spanning regions across Japan (@fig-map). Variations in latitude and longitude are expected to influence blooming times, largely due to their effect on climatic factors such as temperature, sunlight exposure, and climate condition

@@

### Years under Global Warming

Lastly, considering the trend of global climate warming in recent decades, the variable "year" is also included as a random effect in the model. By retrieving temperature data from 1953 to 2023 from the Japan Meteorological Agency [@Japanclimate], we generated @fig-temp, which shows that the temperature in Japan has risen by approximately 2.73 degrees Celsius compared to 1953. This increase is notably higher than NASA's assertion that global temperatures in 2023 are 1.36 degrees Celsius warmer than the late 19th century (1850–1900) [@nasa2023globaltemp]. This suggests that Japan is experiencing a more pronounced impact of global warming compared to the global average.

More data detail could be find in @sec-sam

@@

### Latitude and Longitude with Temperature

@fig-cor illustrates how temperatures vary across different locations based on their geographical coordinates. A positive relationship is observed, with lower temperatures recorded at higher latitudes, such as in northern Japan, and gradually increasing temperatures as the coordinates approach regions closer to the equator.
```{r}
#| label: fig-cor   # For citation in Quarto
#| fig-cap: "Temperature Variation"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center
#| 
# Create a 2D scatter plot with color indicating temperature
ggplot(sakura_data, aes(x = latitude, y = longitude, color = month_mean_temp)) +
  geom_point(size = 3) +
  scale_color_gradient(low = "blue", high = "red") +
  labs(
    title = "Temperature Variation with Latitude and Longitude",
    x = "Latitude",
    y = "Longitude",
    color = "Mean Temp (°C)"
  ) +
  theme_minimal()
```

@@

## Model Selection (Linear Regression and Bayesian Hierarchical Model)

In this study, selecting an appropriate modeling framework is important to ensure accurate predictions and meaningful interpretations of the sakura flowering dates.

@@

## Model set-up

This study uses a Bayesian Hierarchical Linear Regression model to analyze the relationship between sakura flowering dates and various predictors, implemented using the stan_glmer function from the rstanarm package @rstanarm in R [@citeR], with the default priors provided by rstanarm @rstanarm. The analysis_sakura_data dataset is divided into training and testing sets, with 80% allocated for model training and posterior estimation, and the remaining 20% reserved for testing to evaluate predictive performance. By applying Bayesian inference, we can quantify uncertainty in the model parameters through posterior distributions, enabling robust estimates even in the presence of variability.

@@

## Result of the Analysis Data

@fig-rela_result presents the correlation between each predictor variable—latitude, longitude, and monthly mean temperature—and flowering day.

@@

## Result of the Prediction Model

### Performance Overview Analysis

@@

Longitude, by contrast, has a smaller and less certain effect. The coefficient of -0.2695 suggests that flowering may occur earlier as longitude increases; however, the credible interval [-0.7217, 0.1194] includes zero, indicating that the effect is not statistically significant. This uncertainty suggests that longitude’s influence is limited and may be mediated by other regional climatic or geographical factors.

```{r}
#| label: tbl-fix   # For citation in Quarto
#| tbl-cap: "Fixed Effects Coefficients with 95% Credible Intervals"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center

@@

The variance explained by the random effects with adjust \(R^2\) = \(R^2\) = 1.000 confirms that the model perfectly partitions the variability attributed to year and region. Year-based random effects capture temporal patterns,such as the impact of global warming or specific climate anomalies, ensuring that flowering trends align with observed climate changes. Region-based random effects, on the other hand, account for spatial heterogeneity influenced by geographic and environmental differences, such as latitude and local climate conditions. Together, these random effects ensure that the model accurately reflects both temporal and spatial dynamics.

```{r}
#| label: tbl-ram   # For citation in Quarto
#| tbl-cap: "Performance Metrics for Random Effects"  # Caption for the table
#| echo: false  # Suppress code in output
#| warning: false 
#| message: false
#| fig-align: center
#To be note this code is used for preparing the following data, it will not return ant
# === Step 1: Extract Random Effects ===
# Extract station-level and year-level random effects
random_effects <- ranef(flower_model, condVar = TRUE)

@@

## Interpretation

Temperature is considered the most influential predictor of sakura flowering dates, with even minor increases in monthly mean temperatures significantly accelerating blooming. This finding aligns with ecological theories describing phenological shifts driven by global warming. Specifically, a 1°C rise in temperature shifts flowering earlier by an average of 0.33 days, demonstrating the exceptional sensitivity of sakura phenology to climatic variations. It is also a microcosm of the impact of climate change on biological events.

@@

## Sakura Blossom in Modern Situation (1953-2019)

@fig-1953 presents the blooming dates of sakura across Japan from 1953 to 2019( displayed in numeric form as days of the year). Overall data points exhibit a substantial variation. The red smooth trend line indicates a clear shift toward earlier blooming over time, particularly since the late 20th century, imply the influence of global warming on sakura blossom phenology. Notably, the clustering of most data points reflects the inherent stability of Japan's sakura blossom flowering patterns, while significant outliers, such as unusually early blooming events in recent years, may caused by the impact of extreme weather conditions or the introduction of early-blooming sakura blossom varieties.
```{r}
#| label: fig-1953
#| fig-cap: "1953 to 2019 Data (Sourced from Analysis Modern Sakura Data) "
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

## Limitation

Although the model demonstrates strong predictive performance, several limitations must be acknowledged. First, the assumption that all regions respond uniformly to climate variables may oversimplify the complex ecological processes that influence sakura blooming. This approach overlooks important microclimatic variations, such as the urban heat island effect or the unique climates of mountainous regions, which can significantly impact flowering patterns.

@@

## Additional data details {#sec-sam}

### History Data

The historical dataset, shown in @fig-hissam, includes reconstructed March temperatures, the flowering day of the year (DOY), and specific flowering dates for selected years between 812 and 851 CE.
```{r}
#| label: fig-hissam
#| fig-cap: "Sample Historical Sakura Data"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center
# Select a sample of rows from the historical data
sample_history_data <- history_data %>%
  select(year, temp_c_recon, flower_doy, flower_date) %>%
  slice(1:4)  # Select the first 4 rows for demonstration

@@

### Correlation between Each Variable

@fig-heatmap presents the correlation heatmap for the modern sakura dataset, illustrating the relationships between key numerical variables. A notably strong positive correlation (close to 1) is observed between flower_day_in_numeric and full_bloom_day_in_numeric. Latitude and longitude also show moderate to strong positive correlations with flowering indicators, emphasizing the influence of geographic factors on blooming behavior. Among these, latitude exhibits a particularly strong correlation, highlighting its significance in predicting flowering dates.This is consistent with our results in @sec-result. And the variable year showed a weak negative correlation with flowering date, suggesting that flowering may occur earlier in the year under the influence of increasing temperatures due to global warming. 
```{r}
#| label: fig-heatmap
#| tbl-cap: "Correlation Heatmap"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

## Model details {#sec-model-details}

### Posterior predictive check

In @fig-ppcheckandposteriorvsprior we implement a posterior predictive check. The result shows the density overlay plot demonstrates a strong alignment between the observed sakura flowering dates and the model's posterior predictions. The observed density, represented by the dark blue line, closely matches the predictive densities (lighter blue lines) across most of the distribution, indicating that the model captures the central tendency and major patterns effectively. The primary peak around 80 is well-represented, showing the model's strength in predicting the most common flowering dates. Additionally, the secondary peak around 120 aligns reasonably well, suggesting the model's ability to handle more complex patterns, such as bimodal distributions. However, slight discrepancies are observed in the tails of the distribution, particularly below 40 and above 140, where the predictive densities deviate from the observed data. These divergences indicate potential challenges in capturing extreme values or outliers, which may be addressed by including additional predictors, such as microclimatic conditions or species-specific traits.

```{r}
#| eval: true
#| echo: false
#| label: fig-ppcheckandposteriorvsprior
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
#| warning: false 
#| message: false
#| fig.pos: H

@@

```{r}
#| label: fig-mcmc-convergence
#| fig-cap: "MCMC Convergence Diagnostics"
#| fig-subcap: ["Trace Plot for Key Parameters", "R-hat Diagnostics"]
#| echo: false
#| warning: false 
#| message: false
